---
title: "k-Means for clustering"
author: "Nikhil Reddy Addula"
date: "2022-11-05"
output:
  html_document:
    df_print: paged
  pdf_document: default
---

```{r}
#Importing the Dataset
library(readr)
PharmaC <- read_csv("~/Documents/assignments/FUNDAMENTALS ML/PharmaCeuticals.csv")
summary(PharmaC)
str(PharmaC)
```


```{r}
#Loading the Packages
library(dplyr)
library(caret)
library(factoextra)
library(tidyverse)
library(cluster)
library(gridExtra)
```

```{r}
#a. Cluster the 21 companies using only the numerical variables (1–9). Justify the numerous decisions taken throughout the cluster analysis, including the weights assigned to various variables, the particular clustering algorithm(s) utilized, the number of clusters created, and more.

#Removing the dataset's null values and choosing the monetary variables.
colSums(is.na(PharmaC))
row.names <- PharmaC[,1]
PharmaC_data_n<- PharmaC[, 3:11]
head(PharmaC_data_n)
```

```{r}
# Scaling and Normalisation of dataset.
PharmaC_scale <- scale(PharmaC_data_n)
head(PharmaC_scale)
n_data <- as.data.frame(scale(PharmaC_data_n))
```

```{r}
# Calculate K-means clustering for various centers, use a variety of K values, and compare the results.
kmeans_1n <- kmeans(PharmaC_scale, centers = 2, nstart = 30)
kmeans_2n<- kmeans(PharmaC_scale, centers = 5, nstart = 30)
kmeans_3n<- kmeans(PharmaC_scale, centers = 6, nstart = 30)
Plot_1r<-fviz_cluster(kmeans_1n, data = PharmaC_scale)+ggtitle("k=2")
Plot_2r<-fviz_cluster(kmeans_2n, data = PharmaC_scale)+ggtitle("k=5")
Plot_3r<-fviz_cluster(kmeans_3n, data = PharmaC_scale)+ggtitle("k=6")
grid.arrange(Plot_1r,Plot_2r,Plot_3r, nrow = 3)
```

```{r}
dis<- dist(PharmaC_scale, method = "euclidean")
fviz_dist(dis)
```

```{r}
# Estimating the  number of clusters
# Elbow Method is used in scaling the data to determine the value of k
fviz_nbclust(n_data, FUNcluster = kmeans, method = "wss") + labs(subtitle = "Elbow Method")

```

```{r}
# Silhouette Method is used in scaling the data to determine the number of clusters
fviz_nbclust(n_data,FUNcluster = kmeans,method = "silhouette")+labs(subtitle="Silhouette Method")
```

```{r}
# Final analysis and Extracting results using 5 clusters and Visualize the results
set.seed(300)
final_C<- kmeans(PharmaC_scale, 5, nstart = 25)
print(final_C)
```
```{r}
clusplot(PharmaC_scale,final_C$cluster, color = TRUE, labels = 2,lines = 0)
```

```{r}
#b) Interpret the clusters with respect to the numerical variables used in forming the clusters.

#Cluster 1 - 1,3,4,7,10,16,19,21 ( lowest Market_Cap,lowest Beta,lowest PE_Ratio,highest Leverage,highest Rev_Growth.)

#Cluster 2 - 6, 8, 12 (lowest Rev_Growth,highest Beta and levearge,lowest Net_Profit_Margin)

#Cluster 3 - 5, 9, 14, 20 (lowest PE_Ratio,highest ROE,lowest ROA,lowest Net_Profit_Margin, highest Rev_Growth)

#Cluster 4 - 2, 18 (lowest Beta,lowest Asset_Turnover, Highest PE Ratio)

#Cluster 5 - 11, 13, 15, 17 (Highest Market_Cap,ROE, ROA,Asset_Turnover Ratio and lowest Beta/PE Ratio)

PC_Cluster <- PharmaC[,c(12,13,14)]%>% mutate(clusters = final_C$cluster)%>% arrange(clusters, ascending = TRUE)
PC_Cluster

```


```{r}
#Task3
#In terms of the numerical, are there any clusters that exhibit a pattern. (10 to 12) variables? (those n not utilized in the cluster formation).
 

plot1_nr<-ggplot(PC_Cluster, mapping = aes(factor(clusters), fill=Median_Recommendation))+geom_bar(position = 'dodge')+labs(x ='No of clusters')
plot2_nr<- ggplot(PC_Cluster, mapping = aes(factor(clusters),fill = Location))+geom_bar(position = 'dodge')+labs(x ='No of clusters')
plot3_nr<- ggplot(PC_Cluster, mapping = aes(factor(clusters),fill = Exchange))+geom_bar(position = 'dodge')+labs(x ='No of clusters')
grid.arrange(plot1_nr, plot2_nr, plot3_nr)  

```

#As per graph:- 

#Cluster 1 :In this cluster, which also includes distinct Hold, Moderate Buy, Moderate Sell, and Strong Buy medians, the Hold median is the highest. They are from the US, the UK, and Switzerland and are traded on the NYSE.

#Cluster 2:AMEX, NASDAQ, and NYSE all have an equal distribution of companies, but there is a clear Hold and Moderate Buy median as well as a different count between the US and Germany.

#Cluster 3: listed on the NYSE, has distinct counts for France, Ireland, and the US, and has medians for buy and sell orders that are equally moderate.

#Cluster 4: has the same hold and moderate buy medians and is spread out across the US, UK, and listed in.

#Cluster 5: #exclusively listed on the NYSE, evenly distributed across the US and Canada, with medians of Hold and Moderate Buy.

#With respect to media Recommendation Variable ,the clusters follow a particular pattern:
#Cluster 1 and Cluster 2 has Hold Recommendation.
#Cluster 3, Cluster 4and Cluster 5 has moderate buy Recommendation.



```{r}
# (d) Give each cluster a suitable name using any or all of the dataset's variables.

#Cluster 1 :-  HIGH HOLD CLUSTER
#Cluster 2 :- HOLD CLUSTER
#Cluster 3 :- BUY-SELL CLUSTER
#Cluster 4 :- HOLD-BUY CLUSTER
#Cluster 5 :- HOLD-BUY CLUSTER
```

